Paper 1 Notebook

### 2024-01-03 minos/outcomes/paper_1_notebook.Rmd
adding more MICE plots

>>>>

```{r mar_analyses}

aux_vars <- c("SF_12",
              #"SF_12p",
              #"smoker",
              "nkids",       
              "behind_on_bills",
              "financial_situation",
              "future_financial_situation",
              "likely_move",
              "ghq_depression",
              "ghq_happiness",
              "clinical_depression", 
              "scsf1",
              "health_limits_social")
ggmice::plot_corr(mice.data[, aux_vars])

pre.mice.lm <- lm(mice_formula_string, data=mice.data, weights = weight)
forest_plot(pre.mice.lm , paste0(save.path,'mice_SF12_forest.pdf'))
qq_plot(resid(pre.mice.lm ), paste0(save.path, "mice_qq.pdf"))

# writing coefficients table for MICE. 
# is there a version for pool table?
write_coefs <- T
if (write_coefs)
{
  texreg_file <- paste0(save.path, 'SF12_without_MICE_OLS_coefficients.txt')
  tex_label <- paste0("table: without_MICE_OLS_coefficients") 
  tex_headers <- c(texreg::names2latex("Without MICE SF_12 OLS"))
  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "without_mice"))    
  texreg(mice.lm.object, # what model to save coefs for. 
         file=texreg_file,  # where to save.
         custom.model.names = tex_headers, # title of table.
         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
         digits=4, # p values significant figures.
         caption=tex_caption, # \caption command option. 
         label = tex_label, # \label command option. 
         dcolumn=T,# nice column alignment. 
         booktabs=T, # nice hlines. (recommended)
         tabular=T,# tabular env.
         single.row = T, # nicer one row formatting.
         longtable=T, # allows tables to wrap over pages
         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
         fontsize='small') # small font
